---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# FinancialsR

<!-- badges: start -->
<!-- badges: end -->

The goal of FinancialsR is create a pipeline to easily bring SEC corporate financial documents into R for quick analysis. In order to support this there are a number of functions that streamline technical analysis of stock price dynamics in addition to the core features which report the overall strength or weakness of a company's core financial health.

## Installation
#> You can install the released version of FinancialsR from [CRAN](https://CRAN.R-project.org) with:

You can install a working version of FinancialsR its [GitHub](https::github.com/loganstunda/financialsR) repository with:

``` r
devtools::install_github("loganstunda/FinancialsR")
install.packages("FinancialsR")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# library(FinancialsR)

# To do
```


